Colorism and Cosmetics: Investigating Limited Shade Ranges in the Beauty Industry in Japan and India

### 2023-04-21 outputs/paper/paper.qmd
Final Commit

#Create table to summarize lightness range

 summary <- brand_origin |>
  tabyl(group, light_range) |>
  adorn_totals("col")

@@

summary |>
  kable(caption = "Table 1: Total number of products by lightness range in India & Japan") |>
  kable_styling(full_width = F) |>
  add_header_above(c(" " = 1, "Lightness Range" = 6))

@@

The dataset comprises 9 distinct brands for India and 8 for Japan. Table 2 indicates that Japan features a greater number of shades compared to India. Nevertheless, both countries exhibit a similar pattern of maximum product offerings in the 70-80 shade range, followed by the 80-90 range as the second-highest, and subsequently the 60-70 and 50-60 ranges. Notably, only one product belonging to India is classified in the 20-30 shade range, while Japan has none. Furthermore, the table demonstrates that Japan and India share a comparable distribution of lightness among their product ranges.

@@

brand_origin |>
  ggplot(aes(x = group, y = L, fill = origin)) +
  geom_boxplot() +
  scale_y_continuous(breaks=seq(0, 100, 5)) +
  theme_minimal() +
  labs(x = "Country",
    y = "Lightness",
    title = "Fig. 1: Shade Distribution by Lightness: Domestic vs. International Brands",
    color = "Country",
    caption = "Data source: The Pudding.")
```

@@

brand_origin |>
  ggplot(aes(x = group, y = S, fill = origin)) +
  geom_boxplot() +
  scale_y_continuous(breaks=seq(0, 1, 0.05)) +
  theme_minimal() +
  labs(x = "Country",
    y = "Saturation",
    color = "Country",
    title = "Fig. 2: Shade Distribution by Saturation: Domestic vs. International Brands",
    caption = "Data source: The Pudding")

@@

# Results

@@

kbl(summary, caption = "Table 2: Linear Regression Model Summary") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

@@

This study employed a linear regression model to investigate the association between the lightness (L) and saturation (S) of foundation shades offered by popular makeup brands in Japan and India. As presented in Table 2, the model yielded an estimated intercept of 100.31483, indicating that the expected lightness of foundation shades when saturation is zero is 100.31483. The model also revealed a statistically significant negative regression coefficient of -60.59635 for saturation (t = -12.98632, p < .001), indicating a significant negative linear relationship between saturation and lightness of foundation shades.

@@

brand_origin |>
  filter(group == 'Japan') |>
  ggplot(aes(L, S)) +
  geom_point(size = 0.2) +
  facet_wrap(vars(brand)) +
  scale_x_continuous(breaks=seq(50, 100, 5)) +
  theme_minimal() +
   labs(x = "Lightness",
    y = "Saturation",
    title = "Fig. 4: Relationship between Lightness and Saturation in Shades in Japan",
    caption = "Data source: The Pudding")

@@

brand_origin |>
  filter(group == 'India') |>
  ggplot(aes(L, S)) +
  geom_point(size = 0.5) +
  facet_wrap(vars(brand), scales = "free") +
  theme_minimal() +
   labs(x = "Lightness",
    y = "Saturation", 
    title = "Fig. 5: Relationship between Lightness and Saturation in Shades in India",
    caption = "Data source: The Pudding")

>>>>

#Create table to summarize lightness range 
summary <- brand_origin |>
  tabyl(group, light_range) |>
  adorn_totals("col")

@@

summary |>
  kable(caption = "Total number of products by lightness range in India and Japan") |>
  kable_styling() |>
  add_header_above(c(" " = 1, "Lightness Range" = 6))

@@

The dataset comprises 9 distinct brands for India and 8 for Japan. Table 1 indicates that Japan features a greater number of shades compared to India. Nevertheless, both countries exhibit a similar pattern of maximum product offerings in the 70-80 shade range, followed by the 80-90 range as the second-highest, and subsequently the 60-70 and 50-60 ranges. Notably, only one product belonging to India is classified in the 20-30 shade range, while Japan has none. Furthermore, the table demonstrates that Japan and India share a comparable distribution of lightness among their product ranges.

@@

brand_origin |>
  ggplot(aes(x = group, y = L, fill = origin)) +
  geom_boxplot() +
  scale_y_continuous(breaks=seq(0, 100, 5)) +
  theme_minimal() +
  labs(x = "Country",
    y = "Lightness",
    caption = "Fig. 1: Shade Distribution by Lightness: Domestic vs. International Brands",
    color = "Country") 
```

@@

brand_origin |>
  ggplot(aes(x = group, y = S, fill = origin)) +
  geom_boxplot() +
  scale_y_continuous(breaks=seq(0, 1, 0.05)) +
  theme_minimal() +
  labs(x = "Country",
    y = "Saturation",
    color = "Country",
    caption = "Fig. 2: Shade Distribution by Saturation: Domestic vs. International Brands")

@@

# Results
This study employed a linear regression model to investigate the association between the lightness (L) and saturation (S) of foundation shades offered by popular makeup brands in Japan and India. As presented in Table 2, the model yielded an estimated intercept of 100.31483, indicating that the expected lightness of foundation shades when saturation is zero is 100.31483. The model also revealed a statistically significant negative regression coefficient of -60.59635 for saturation (t = -12.98632, p < .001), indicating a significant negative linear relationship between saturation and lightness of foundation shades.
```{r}
#| messages: false
#| echo: false
#| warning: false

@@

kbl(summary, caption = "Linear Regression Model Summary") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

@@

@@

brand_origin |>
  filter(group == 'Japan') |>
  ggplot(aes(L, S)) +
  geom_point(size = 0.2) +
  facet_wrap(vars(brand)) +
  scale_x_continuous(breaks=seq(50, 100, 5)) +
  theme_minimal() +
   labs(x = "Lightness",
    y = "Saturation",
    caption = "Fig. 4: Relationship between Lightness and Saturation in Shades in Japan")

@@

brand_origin |>
  filter(group == 'India') |>
  ggplot(aes(L, S)) +
  geom_point(size = 0.5) +
  facet_wrap(vars(brand), scales = "free") +
  theme_minimal() +
   labs(x = "Lightness",
    y = "Saturation", 
    caption = "Fig. 5: Relationship between Lightness and Saturation in Shades in India")
